---
title: "Sampling Theory and Survey Design"
author: "Wenhui Zeng"
date: '`r format(Sys.Date(), format="%b %d, %Y")`'
output:
  slidy_presentation: default
  beamer_presentation:
    fig_height: 3
    fig_width: 4
    incremental: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##Introduction

  -The survey is designed to assess the dietary habits and nutritional knowledge of       college students
  
  -Help to bring about an improvement of the nutritional situation of college students
  
  -Evaluation of the nutritional effect of a project/program on the improvement of       health dietary
 
  
## Results

###Daily Fruit Uptaken

*During the past 7 days, how many times did you eat fruit?*

```{r echo = FALSE, message=FALSE, warning=FALSE, error=FALSE,results="hide", fig.align='center'}
data<-c(3,7,1)
labels<-c("Less than one time","One time","Two times")
barplot(data,ylim=c(0,10),xlim=c(0,10),width=2,space=0.5,ylab="Number of People",las=1,
        main = "Daily Fruit Uptaken")
text(x=seq(2,10.9,by=3),y=-0.15,adj=1, srt = 45,labels = labels,xpd=T,cex=0.8)
text(2,4,labels="3",font=1)
text(5,8,labels="7",font=1)
text(8,2,labels="1",font=1)
```


##Results

###Daily vegetables Uptaken

*During the past 7 days, how many times did you eat vegetables*

```{r echo = FALSE, message=FALSE, warning=FALSE, error=FALSE,results="hide", fig.align='center'}
data_1<-c(1,1,4,4,1)
labels_1<-c("I did not eat vegetables",
        "Less than one time",
          "One time",
          "Two times",
          "Three times")
barplot(data_1,ylim=c(0,10),width=2,space=0.2,ylab="Number of People",las=1,
        main = "Daily Vegetables Uptaken")
text(x=seq(1.5,11.5,by=2.5),y=-0.15,adj=1, srt = 45,labels = labels_1,xpd=T,cex=0.7)
text(1.5,2,labels="1",font=1)
text(3.8,2,labels="1",font=1)
text(6.3,5,labels="4",font=1)
text(8.5,5,labels="4",font=1)
text(11,2,labels="1",font=1)
```

## Result

###Nutrition Knowledge

*Have you take any nutrition related class in the past?*

```{r echo = FALSE, message=FALSE, warning=FALSE, error=FALSE,results="hide", fig.align='center'}
data_2<-c(8,3)
labels_2<-c("No","Yes")
barplot(data_2,ylim=c(0,10),width=2,space=0.2,ylab="Number of People",las=1,
        main = "Ever Taken Nutrition Class")
text(x=seq(1.5,6.5,by=2.5),y=-1,adj=1,labels = labels_2,xpd=T,cex=0.8)
text(1.3,9,labels="8",font=1)
text(3.8,4,labels="3",font=1)
```

## Result

###Nutrition Knowledge

*How much do you agree or disagree with the following sentence? *

 *"Fruits are a good source of vitamins and should be included in a daily diet."*
 
```{r echo = FALSE, message=FALSE, warning=FALSE, error=FALSE,results="hide", fig.align='center'}
par(mfrow=c(1,1))
library(vcd)  
slices<-c(5,4,2) 
pct<-round(slices/sum(slices)*100)
lbls<-c("Strongly Agree","Agree","Somewhat Agree")  
lbls2<-paste(lbls,"\n",pct,"%",sep = "")
pie(slices,labels = lbls2,col=rainbow(length(slices)),cex=0.8,clockwise = T)

```


##Result

###Nutrition Knowledge

 *How much do you agree or disagree with the following sentence?*
 
   *"Vegetables are a good source of fiber and should be included in a daily diet."*

```{r echo = FALSE, message=FALSE, warning=FALSE, error=FALSE,results="hide", fig.align='center'}
par(mfrow=c(1,1))
slices<-c(7,3,1) 
pct<-round(slices/sum(slices)*100)
lbls<-c("Strongly Agree","Agree","Somewhat Agree")  
lbls2<-paste(lbls,"\n",pct,"%",sep = "")
pie(slices,labels = lbls2,col=rainbow(length(slices)),cex=0.8,clockwise = T)
```

##Discussion

  -72% of the subjects have fruit at least one time per day. All the students eat     
  fruit in the past 7 days.
  
  -82% of the subjects have vegetables at least one time per day. 91% of the subjects   eat vegetables in the past 7 days.
  
  -Only 27% of the subjects has taken nutrition-related class. 
  
  -All the subjects are agree with the fruit and vegetables should be included in    
  daily diet.
  
  -People are tend to more agree that vegetables are a source of fiber should be    
  include in the daily diet
  
  -We can take some possible intervention to provide a health diet environment














